---
title: "EOBS using R"
author: "Martin Roth"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{EOBS using R}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

This doucment presents an simple example of a national climate monitoring using EOBS and eobsR.
The idea is that one can do a national analysis using the following steps:

- specify a certain variable
- specify a time period
- load a country shape file using database ...
- load the corresponding data with eobsR
- do the analysis, e.g., using rClimDex
- put this into a shiny app (with slider for index and country)

## Mean temperature in the Netherlands for 2014
```{r}
library(eobsR)
library(ggplot2)
adm0 <- raster::getData('GADM', country='NL', level=0)
fadm0 = fortify(adm0)
data  <- importEOBS('tg', '2014', adm0, "grid")
meanData <- data[, .(TGG = mean(tg)), by = .(lon, lat)]
```

```{r, fig.show='hold'}
ggplot(fadm0, aes(x = long, y = lat, group = group)) +
  geom_path() +
  coord_map() +
  geom_tile(aes(x =lon, y = lat, fill = TGG, group = NULL),
            alpha=0.5,
            data = meanData) +
  scale_fill_distiller(type='div', palette='RdBu', trans='reverse',
                       guide = guide_legend(reverse=TRUE))
```

## Mean temperature in the Netherlands and Belgium for 2014
```{r}
library(eobsR)
library(ggplot2)
library(sp)
adm01 <- raster::getData('GADM', country='NL', level=0)
adm02 <- raster::getData('GADM', country='Belgium', level=0)
adm0  <- rbind(as(adm01, 'SpatialPolygons'), as(adm02, 'SpatialPolygons'), makeUniqueIDs=TRUE)
fadm0 = fortify(adm0)
data  <- importEOBS('tg', '2014', adm0, "grid")
meanData <- data[, .(TGG = mean(tg)), by = .(lon, lat)]
```

```{r, fig.show='hold'}
ggplot(fadm0, aes(x = long, y = lat, group = group)) +
  geom_path() +
  coord_map() +
  geom_tile(aes(x =lon, y = lat, fill = TGG, group = NULL),
            alpha=0.5,
            data = meanData) +
  scale_fill_distiller(type='div', palette='RdBu', trans='reverse',
                       guide = guide_legend(reverse=TRUE))
```

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
